Finding Quality Issues in SKOS Vocabularies

### 2012-03-29 criteria.tex
fixed todos for section 3

% Origin and rationale
Allemang et al. \cite{Allemang2011} propose to ``not indicate any concepts internal to the tree as top concepts'', which means that top concepts should not have broader concepts. 
% Function definition
Affected resources can be found by iterating over all \texttt{skos:TopConcept}s and collecting those that are related to a resource via a \texttt{skos:broader} property.

\todo{CM}{check top concept issue!}

@@

% Origin and rationale
SKOS concepts become linkable resources, when vocabularies are being published on the Web. Estimating the number of in-links and identifying the concepts without any in-links, can be an important indicator for the importance of a concept.
% Function definition
To estimate the number of in-links we only consider the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace. \todo{CM}{given an example for an authoritative concept, maybe from LCSH} The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part. Empty query results are indicators for missing in-links and are thus included in the result set of this function.

@@

% Origin and rationale
In the Linked Data context, SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}. Similar to \emph{Missing In-Links}, this issue identifies the set of all authoritative concepts that have no out-links.
% Function definition
It can be computed by iterating over all elements $ac \in AC$ and checking the host part of all related resource URIs \todo{CM}{authoritative concepts?}. If none of these host names differ from the host part of $ac$'s URI, it has no out-links and is thus included in the resources identified by this issue.

>>>>

% Origin and rationale
Allemang et al. \cite{Allemang2011} propose to ``not indicate any concepts internal to the tree as top concepts'', which means that top concepts should not have broader concepts. 
% Function definition
Affected resources can be found by iterating over all top concepts and collecting those that are related to a resource via a \texttt{skos:broader} property that is no \texttt{skos:mappingRelation}.

@@

% Origin and rationale
SKOS concepts become linkable resources, when vocabularies are being published on the Web. Estimating the number of in-links and identifying the concepts without any in-links, can be an important indicator for the importance of a concept.
% Function definition
To estimate the number of in-links we only consider the set of ``authoritative concepts'' $AC \subseteq C$, which consists of all concepts that are identified by URIs in the vocabulary namespace. For example, \texttt{PXV} links the concept \url{http://www.peroxisomekb.nl/v1.6/pxv/C000297} to \url{http://www.bioexpert.nl/mesh/2010/concept/M0028264} using \texttt{skos:closeMatch}. Both resources can be infered as being \texttt{skos:Concept}s, but the latter is no authoritative concept because it's URI doesn't belong to the \texttt{PXV} namespace. The number of in-links referencing an authoritative concept can be estimated by iterating over all elements in $AC$ and querying the Sindice\footnote{\url{http://sindice.com/} indexes structured Web data and covers approximately 230M documents with over 11 billion triples} SPARQL endpoint for triples containing the concept's URI in the object part. Empty query results are indicators for missing in-links and are thus included in the result set of this function.

@@

% Origin and rationale
In the Linked Data context, SKOS concepts should be linked with other related concepts on the Web, ``enabling seamless connections between data sets''\cite{Heath2011}. Similar to \emph{Missing In-Links}, this issue identifies the set of all authoritative concepts that have no out-links.
% Function definition
It can be computed by iterating over all elements $ac \in AC$ and checking the URIs of all related resources. If none of these URI's namespace differs from the namespace of $ac$'s URI, $ac$ has no out-links and is thus included in the resources identified by this issue.
